\PaperTitle

### 2024-05-04 Final_Report/paper.tex

\subsection{Employed models}
For this project, we required a classification model that would be able to accurately predict the website of origin for a given packet. We chose to employ three different models: K-Nearest Neighbors, Random Forest, and Neural Network. The reason we had selected more than one model was to be able to effectively compare the performance of each and determine which was the most effective for our solution. 
These models were chosen for their abilities to classify data and their potential to accurately predict the website of origin for a given packet. We also used a baseline model, Logistic Regression, to also compare the performance of the other models to a more simple, linear model.
\subsubsection{Logistic Regression (Baseline)}
As a starting point, we employed the Logistic Regression model as a baseline for our data analysis. Logistic regression is a statistical method used for binary classification tasks, where the goal is to predict the probability of an event happening or not happening.
It was understoof initiallly that this model may not be an ideal fit for our data; due to the regressions binary nature having more than two classifications is not ideal.

Characteristics of Logistic Regression:
\begin{enumerate}
  \item \textbf{Binary Outcome}: Logistic regression is used for binary classification tasks, where the outcome variable has only two possible outcome
  \item \textbf{Linear Relationship}: Logistic regression assumes a linear relationship between the independent variables and the log-odds of the outcome
  \item \textbf{Probablistic Output}: Instead of predicting discrete classes directly, logistic regression predicts the probability that a given observation belongs to a particular class
  \item \textbf{Interpretability}: Logistic regression coefficients represent the change in the log-odds of the outcome for a one-unit change in the corresponding independent variable, making it easy to interpret the impact of each variable on the outcome. This characteristic was especially important for our baseline
\end{enumerate}

@@

\subsubsection{Random Forest}
A Random Forest is a form of an ensemble model that is composed of multiple decision trees. Each tree is ran and gives its predicted classification, and the final classification is determined by a majority vote of all the trees (seen in figure 3).

Advantages of Random Forest Models:
\begin{enumerate}
  \item \textbf{Ability to handle complex features}: Random forests have the ability to handle complex features, such as time and protocols in the case of network packets, and the relationships between them, which can be very important in classifying network traffic.
  \item \textbf{High accuracy}: Random forests diminishes the problem of overfitting that can occur in decision trees, and can achieve higher accuracy, helping to more accurately determine website origins of a packet.
  \item \textbf{Feature importance}: Random forests can provide insight into which features are most important in the classification process, such as protocol vs time in classifying websites for this project.
  \item \textbf{Scalability}: Random forests can be scaled to handle much larger datasets, which can be very important for network traffic which can receive a high volume of packet data extremely quick.
\end{enumerate}

The library used for the Random Forest model was scikit-learn \cite{scikit-learn}. Sci-kit learn's implementation of Random Forests utilize aggregation to take a soft vote of the soft classifications (probability of the packet being from each class). Within soft voting, a weighted average of the probabilities from the classification are taken, and the class with the highest probability is chosen as the final classification.

\begin{figure}[h!]
  \centering
  \includegraphics[width=9cm]{Figures_and_Graphs/RandomForestExample.png}
  \caption{Random Forest model structure example}
  \label{fig:RFExample}
\end{figure}

\subsubsection{Neural Network}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets. Later, goes on to determine the model which best classified our selected websites based on network packet data.
\subsection{Dataset}
\subsection{Evaluation Metrics}
Accuracy and Macro F1 score were the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
\\
Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).

>>>>

\subsection{Employed models}
\subsubsection{Logistic Regression (Baseline)}

@@

\subsubsection{Random Forest}

\subsubsection{Neural Network}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets. Later, goes on to determine the model which best classified our selected websites based on network packet data.
\subsection{Dataset}
\subsection{Evaluation Metrics}
Accuracy and Macro F1 score were the primary metrics used to evaluate each model. These metrics are applicable to all models and allow for
a direct comparison for each of their performances. Two other metrics: precision and recall, help to provide a more detailed understanding of the model's performance on a class-to-class basis.
\newline \\
The equation for \textbf{Accuracy}: \\
\[
Accuracy= \frac{TP + TN}{TS}
\]
\newline \\
The equation for \textbf{Macro F1}: \\
\[
Macro F 1= \frac{1}{n} \sum_{1}^{n} \frac{2*Precision_i*Recall_i}{Precision_i+Recall_i}
\]
\newline \\
The equation for \textbf{Recall}: \\
\[
Recall= \frac{TP}{TP + FN}
\]
\newline \\
The equation for \textbf{Precision}: \\
\[
Accuracy= \frac{TP}{TP + FP}
\]
Accuracy is the score that rates the effectiveness of a model at classification overall (ie. how many it predicted correctly out of the total set).
